Model LF

### 2022-11-16 max_dp endogen stød.Rmd
Commit

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

# Scenario 7 All but prod and lf

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

@@

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3

### Unemployment rate

@@

@@

>>>>

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

# Scenario 7 All but prod and wage

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

**Macro effect without productivity and wage**

@@

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3
macro_elas_nowage= -0.04
### Unemployment rate

@@

### Case 3

@@

### Case 3 no wage

marg_gain_c3_w= sigma*(comp_r_sfc);marg_gain_c3

marg_cost_c3_w= (micro_elas_dørs +macro_elas_nowage )/(1-ur_fag); marg_cost_c3_w
